Title

### 2023-09-17 cover_letter_plos.tex
these confounded tests drive me nuts
Contestando mas comentarios / simulacion mapas dinamicos

\documentclass[12pt, addrfooterall, english]{if_letter_2013}
% \usepackage[spanish]{babel} 
\usepackage[utf8]{inputenc}
% \date{17 de Octubre de 2018}
\begin{document}
\begin{letter}{
.\vspace{-2cm}
% PLOS One\\
% Editorial 
% \adirectorcecilia
% \aquieninterese
% \apapiitmendoza
% \aconacytGelover
% \asecretariomostalac
% Dra. Maria del Carmen de la Peza Casares\\
% Directora Adjunta de Desarrollo Científico y Secretaria Técnica del FONCICYT\\
% CONACYT
}
\opening{To whom it may concern}

@@

We declare the manuscript’s originality and exclusivity for publication. In
addition, we have not had any prior interactions with PLOS regarding this
manuscript. In the event that our manuscript is chosen for review, we kindly
suggest Dr. Fabio Sciarrino as a suitable reviewer, given his background and
expertise to evaluate our findings. We have no objections to any other
potential reviewers.

Each named author has significantly contributed to the research and preparation
of this manuscript. Furthermore, the named authors have no conflicts of
interest to disclose.

% Thank you for considering our work.
% On behalf of all authors

>>>>

\documentclass[12pt, addrfooterall, english]{if_letter_2013}
% \usepackage[spanish]{babel} 
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

% \date{17 de Octubre de 2018}
\begin{document}
\begin{letter}{
.\vspace{-2cm}
% PLOS One\\
% Editorial 
% \adirectorcecilia
% \aquieninterese
% \apapiitmendoza
% \aconacytGelover
% \asecretariomostalac
% Dra. Maria del Carmen de la Peza Casares\\
% Directora Adjunta de Desarrollo Científico y Secretaria Técnica del FONCICYT\\
% CONACYT
}
\opening{To whom it may concern}

@@

All relevant data and codes to replicate the results can be found in the following
public repository \href{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}.

We declare the manuscript’s originality and exclusivity for publication. In
addition, we have not had any prior interactions with PLOS regarding this
manuscript. In the event that our manuscript is chosen for review, we kindly
suggest Dr. Fabio Sciarrino as a suitable editor, given his background and
expertise to evaluate our findings. We have no objections to any other
potential reviewers.

Each named author has significantly contributed to the research and preparation
of this manuscript. Furthermore, the named authors have no conflicts of
interest to disclose. Both authors received support from projects CONAHCyT 
(Consejo Nacional de Humanidades, Ciencias y Tecnologías
\href{https://dgapa.unam.mx/index.php/impulso-a-la-investigacion/papiit}{https://dgapa.unam.mx/index.php/impulso-a-la-investigacion/papiit}) 285754, 
and UNAM-PAPIIT  (Universidad Nacional Autónoma de México - Programa de Apoyo a 
Proyectos de Investigación e Innovación Tecnológica \href{https://conahcyt.mx/}{https://conahcyt.mx/}) IG101421.
The funders had no role in study design, data collection and analysis, 
decision to publish, or preparation of the manuscript.
